---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
#
```

# instatCalculations

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

This repository contains R6 classes and supporting functionality for the calculation system used in [R-Instat](https://github.com/IDEMSInternational/R-Instat). This package serves as a core component of the R-Instat calculation system.

## Installation

You can install the development version of instatCalculations from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github("IDEMSInternational/instatCalculations")
```

## Contributing

We welcome contributions to improve this package! To contribute:
  
1. Fork the repository.
2. Create a new branch for your feature or bug fix.
3. Submit a pull request with a clear description of your changes.

## License

This project is licensed under the GNU LGPL v3.0 License. See the LICENSE file for details.

## About

This package is developed and maintained by IDEMS International as part of the R-Instat project. For more information, visit our [website](https://idems.international/).

---
  
  If you have any questions or issues, feel free to open an issue on the repository or contact us directly.